---
title: "week_05_notes"
author: "Andrew Nalundasan"
date: "10/27/2021"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# load libraries
library(readxl)
library(forecast)
```

## Overview Video 

+ continue studying MA model

+ Inverted MA Roots

    + MA process is always stationary, but may not always be invertible
    + Invertiblity: express past data using an AR model
        + If current value can be expressed by past value or not
        + Inverted MA Root < 1 then this is invertible
    + increasing horizon does something to the forecast
    + MA model is a short memory model

+ good time for DTC team to come together

    + think of question that we want to answer
    + get dataset
    + start exploration of TS

## Lecture Video

1. MA(2) process is stationary

+ a bunch of maths stuff

+ assume Eps_t is a normal distribution

+ variance is not a function of time. it's a constant

+ covariance 

+ correlation

+ for h > 2, rho(h) == 0

    + more than 2 periods apart, correlation becomes 0
    + no terms of epsilon are the same
    
2. Optimal forecast of MA(2) process

+ when h == 1


3. Optimal forecast of MA(2) process

+ when h == 2

+ calculate forecast

+ calculate forecast error

+ calculate variance

+ calculate variance error

4. Optimal forecast of MA(2) process

+ when h > 2

+ I_t (Information t) has prediction power or not

+ unconditional variance of random variable y_t

+ density forecast: 

    + f(yt+3 | I_t) ~ N(mu_t+3|t, sigma**3_t+3 | t)
    + N <- Normal distribution






